Macroscopic Salt Rejection through Electrostatically Gated Porous Graphene

### 2019-01-10 paper/SI.tex
Complete SI analysis of delta

Next we seek the value between $R_{\mathrm{PCTE}}$ and
$R_{\mathrm{G}}^{0}$ (ungated resistance of PG), $\delta$ (as defined
in main text Section \ref{main-sec:res-1}). It is pointed out that the
scaling law for $R_{\mathrm{PCTE}}$ and $R_{\mathrm{G}}^{0}$
differs. For a long channel like PCTE, the resistance is derived from
Fick's law as\cite{O_Hern_2014}:
\begin{equation}
\label{eq:R-PCTE}
 R_{\mathrm{PCTE}} = \frac{1}{D} \frac{L}{\pi r_{\mathrm{PCTE}}^{2}}
\end{equation}
whereas $D$ is the diffusivity of the specie, $L$ is the length of
channel ($\sim$24 $\mathrm{\mu}$m), and $r_{\mathrm{PCTE}}$ is the
average radius of the PCTE channels ($\sim$400 nm). On the other hand,
the transport through 2D pore with high radius/thickness ratio falls
into the regime of the Sampson formula \cite{Roscoe_1949}, where the
entrance resistance dominates over the bulk resistance, with the
formula as \cite{Roscoe_1949,Celebi_2014}:
\begin{equation}
  \label{eq:sampson}
  R_{\mathrm{g}}^{0} = \frac{1}{D} \frac{3 \pi}{r_{\mathrm{G}}}
\end{equation}
We therefore estimate the value of $\delta$ as:
\begin{equation}
  \label{eq:delta-resistance}
  \delta = {\displaystyle
    \frac{{\displaystyle \frac{L}
        {\pi r_{\mathrm{PCTE}}^{2}}}}
    {{\displaystyle \frac{3 \pi}{r_{\mathrm{G}}} \frac{1}{\gamma}}}}
  \approx 2.20
\end{equation}

>>>>

Next we seek the value between $R_{\mathrm{PCTE}}$ and
$R_{\mathrm{G}}^{0}$ (ungated resistance of PG), $\delta$ (as defined
in main text Section \ref{main-sec:res-1}). It is pointed out that the
scaling law for $R_{\mathrm{PCTE}}$ and $R_{\mathrm{G}}^{0}$
differs. For a long channel like PCTE, the resistance is derived from
Fick's law as\cite{O_Hern_2014}:
\begin{equation}
\label{eq:R-PCTE}
 R_{\mathrm{PCTE}} = \frac{1}{D} \frac{L}{\pi r_{\mathrm{PCTE}}^{2}}
\end{equation}
whereas $D$ is the diffusivity of the specie, $L$ is the length of
channel ($\sim$24 $\mathrm{\mu}$m), and $r_{\mathrm{PCTE}}$ is the
average radius of the PCTE channels ($\sim$400 nm). On the other hand,
the transport through 2D pore with high radius/thickness ratio falls
into the regime of the Sampson formula \cite{Roscoe_1949}, where the
entrance resistance dominates over the bulk resistance, with the
formula as \cite{Roscoe_1949,Celebi_2014}:
\begin{equation}
  \label{eq:sampson}
  R_{\mathrm{g}}^{0} = \frac{1}{D} \frac{3 \pi}{r_{\mathrm{G}}}
\end{equation}
We therefore estimate the value of $\delta$ as:
\begin{equation}
  \label{eq:delta-resistance}
  \delta
  = \frac{R_{\mathrm{PCTE}}}{R_{\mathrm{G}}^{0}}
  = {\displaystyle
    \frac{{\displaystyle \frac{L}
        {\pi r_{\mathrm{PCTE}}^{2}}}}
    {{\displaystyle \frac{3 \pi}{r_{\mathrm{G}}} \frac{1}{\gamma}}}}
  \approx 2.20
\end{equation}
Alternatively, we may also estimate the range of $\delta$ from
experimental data in main text \Fig{} \ref{main-fig:2}b using the
relation:
\begin{equation}
  \label{eq:exp-delta}
  \delta = \left(\frac{\boldsymbol{J}_{\mathrm{PCTE}}}{\boldsymbol{J}_{\mathrm{PG}}^{0}} -1 \right)^{-1}
\end{equation}
by assuming the validity of the circuit analog model for all salt
systems. We find that the $\delta$ value estimated from the simple
geometric model agrees well with the experimental results. As shown in
\Fig{}, the theoretical estimated value of $\delta$ (organe line) lies
within the margin of the majority of experimental data, which is
exceptionally good given the simplicity of the model used.

Next we show how the effective salt rejection ratio through PG, $\xi$,
is extracted from the experimental $\eta$ values. Using the circuit
analog model, the definition of $\eta$ from main text
Eq. \ref{main-eq:rejection} can be rewritted using transport
resistances as:
\begin{equation}
  \begin{aligned}[t]
      \label{eq:eta-R}
  \eta &= 1 - {\displaystyle
    \frac{(R_{\mathrm{PCTE}} + R_{\mathrm{G}})^{-1}}
    {(R_{\mathrm{PCTE}} + R_{\mathrm{G}}^{0})}} \\
    &= 1 - \frac{\delta + 1}{\delta + R_{\mathrm{G}}/R_{\mathrm{G}}^{0}} \\
    &= 1 - \frac{\delta + 1}{\delta + \chi}
  \end{aligned}
\end{equation}
where we define $\chi = R_{\mathrm{G}}/R_{\mathrm{G}}^{0}$ which
represents the change of the transport resistance through PG upon
gating. Consequentially, the salt rejection ratio $\xi$, is associated
with $\chi$ by $\xi = 1 - \chi^{-1}$. Reformatting Eq. \ref{eq:eta-R}
gives:
\begin{equation}
  \label{eq:xi-deriv}
  \begin{aligned}[t]
    \xi &= 1 - \chi^{-1} \\
    &= \frac{(\delta + 1) \eta}{\delta\eta + 1}
  \end{aligned}
\end{equation}
which is main text Eq. \ref{main-eq:xi-def}. When $0<\eta<1$ (salt
rejection regime) and $\delta>0$, Eq. \ref{eq:xi-deriv} always
guarantees $\xi>\eta$, since $\delta + 1$ is always larger than
$\delta\eta + 1$. In other words, due to the existance of
$R_{\mathrm{PCTE}}$, the effective salt rejection through PG upon gating, is always larger than that expperimentally observed.
